---
title: "Index"
author: "Yangqiuzhe Zhu"
date: '2022-08-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

For this assignment, I choose the data set of Incarceration Trends Dataset from
VERA. In all the data set it provide to me, I choose incarceration_trends.csv as
my main source to analyze the unfair of incarceration. For recent year, people
are pay much more attention on race equality in different aspects like working,
education, or medical condition. For this research, I pay my attention to the
situation of incarceration trends to study the specific problems in the system
which we considered is fair to everyone as we considered before.

## Summary Information
```{r,include=TRUE, echo=FALSE, code = readLines("summary_infomation.R")}
print(summary_info)
```

From the summary information list I get from the dataset above, I found that
during all the population, the population in **Jail**(mean rate is
**4.318663%**) is less than the population in **Prison**(mean rate is 
**6.689772%**). When I focus on gender problems which also been mentioned by
people more frequently recently, I found that in all population, no matter in
Jail or Prison, the average rate of **Male(7.514543%)** is higher than average
rate of **Female(1.0408%)**. After that, I move to the race problems which this
assignment most care about, and I found that the 
**average rate of black people(27.47658%)** is much higher than the 
**average rate of white people(4.463364%) **.

## Trends over time chart
```{r,echo=FALSE, code = readLines("time_chart.R")}
```

For this time trends chart, I compare how the Black and white Ratio change over
time in New York County. The reason Why I choose New York County is because this
county is always the central focus of race problem. The data in this county
can be a good representation for that period of time.

## Variable comparison chart
```{r,echo=FALSE, code = readLines("compare_chart.R")}
```

For this two variable comparison chart, I compare the general situation of
different gender between female and male in Prison. It is easy to find that
the size of female population is relative lower than male population is the
whole history in New York County.

## Map Data
```{r,echo=FALSE, code = readLines("usmap.R")}
```

In this map, I show the average value of Minority Proportion in different
state to give a glimpse to the racial situation in the whole America. From this
map, we can easily tell how serious the inequity of different is in different
state of America.
